---
title: "tlao-main-iCatcher"
author: "Joseph Outa"
date: "2024-02-23"
output:
  bookdown::html_document2:
    toc: true
    toc_depth: 4
    theme: cosmo
    highlight: tango
---

```{r setup, include=FALSE}
library(pacman)
pacman::p_load(
               tidyverse,
               here,
               bookdown,
               lmerTest,
               performance
               )
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
options(scipen = 1, digits = 3)
sessionInfo()
library(plotly)

```

## Read and clean data

```{r, message = FALSE}
here()
d_icatcher_raw <- read_csv(here("analysis_data/FULLSTUDY_processed_lookdata_byTrial-0920.csv")) %>% 
  mutate(Log_looks = log(Looks.duration_onLooks))

#raed pyhab data. Only need for sanity check + grabbing age data
directory_path <- here("analysis_data/trial_info")
file_paths <- list.files(path = directory_path, pattern = "^sub-.*\\_trialCondition.csv$", full.names = TRUE) 

d_pyhab <- map_df(file_paths, ~ {read_csv(.x, col_types = cols(
  sex = col_character())) %>% # otherwise sex treated as logical due to 'F'
    mutate(filename = str_remove(basename(.x), "_trialCondition.csv"))  %>% 
    mutate(sID = str_replace(sID, "sub-LIU_TLAO_", "")) %>% #first standardize all sIDs to be short (some are short, some are long)
    mutate(sID = paste0("sub-LIU_TLAO_", sID)) %>% #then lengthen them all
    mutate(sID_equals_filename = sID == filename)  %>% # Check if sID and filename are equal (for data entry errors)
    mutate(sID = if_else(!sID_equals_filename, filename, sID))  %>% # Replace sID with filename if not equal
    mutate(months = case_when(sID == "sub-LIU_TLAO_s044" & months == -5 ~ 6, #fix erroneous months of births 
                            sID == "sub-LIU_TLAO_s053" & months == -5 ~ 6,
                            TRUE ~ months)) }) 

```

pre-exclusion N and age

- N = 57 (tested, if went past setup and showed some parts of stimuli)
- mean age = 6.55 months

```{r}
d_icatcher_raw %>% 
  left_join(d_pyhab %>% 
              select(sID, months, condLabel) %>% 
              distinct(sID, .keep_all = TRUE) %>%  # Keep only unique rows by sID
              rename(SubjectInfo.subjID = "sID"), 
              by = "SubjectInfo.subjID") %>% 
  relocate(months, .after = "SubjectInfo.subjID") %>% 
  mutate(months = ifelse(SubjectInfo.subjID == "sub-LIU_TLAO_s032", 8, months)) %>% 
  mutate(months = ifelse(SubjectInfo.subjID == "sub-LIU_TLAO_s070", 8, months)) %>% 
  summarize(mean_age = mean(months))
```

# Data quality checks, fixes, exclusions

# fix s085 

- s085 was erroneously coded as having LT of 0.0 by icatcher, grabbed and imputed correct data from pyhab coding (confirmed figure)

```{r}
#filter d_icatcher_raw_candidates 
d_icatcher_raw_candidates <- d_icatcher_raw %>%
  filter(Looks.duration_onLooks == 0.0) %>%
  select(-SubjectInfo.sessionNumber) %>%
  filter(Trials.trialType == "test") %>% 
  filter(SubjectInfo.subjID == "sub-LIU_TLAO_s085") #checked each one manually, and s085 s the only one who's LT is erroneously coded as 0 by icatcher. s036 looked for < 3s total, and s029, s055, s059, and s085 were looking away during Attention grabber

#prepare the data from d_pyhab for matching and imputation
d_pyhab_filtered <- d_pyhab %>%
  rename(SubjectInfo.subjID = sID, Trials.ordinal = trial, Looks.duration_onLooks = sumOnA) %>%  # Renaming to match
  filter(GNG == 1) %>%
  semi_join(d_icatcher_raw_candidates, by = c("SubjectInfo.subjID", "Trials.ordinal")) %>%
  select(SubjectInfo.subjID, Trials.ordinal, Looks.duration_onLooks)

#update the values in d_icatcher_raw
d_icatcher_raw_updated <- d_icatcher_raw %>%
  left_join(d_pyhab_filtered, by = c("SubjectInfo.subjID", "Trials.ordinal")) %>%
  mutate(Looks.duration_onLooks = if_else(Looks.duration_onLooks.x == 0.0, Looks.duration_onLooks.y, Looks.duration_onLooks.x)) %>%
  select(-Looks.duration_onLooks.x, -Looks.duration_onLooks.y)  # Clean up temporary columns

#add back in! 
d_icatcher <- d_icatcher_raw_updated

```

## Trial Exclusions and Subject Exclusions

subjects excluded (20):
- technical difficulties (5):  s028, s029, s030, s042, s078 (i.e. stimuli didn't loop, pyhab keeps freezing, no sound, )
- experimenter error (2): s035, s064 (forgetting to record shared screen, not recording session)
- inattention (4): s039, s053, s058, s073
- poor video quality (1): s043
- external distraction (3): s068, s069, s075 (siblings, caregiver)
- trial exclusions resulting in no trials left/accumulated looking time less than 3 seconds (5): s038, s049, s062, s067, s071 (and thus had to exclude non-consecutive test trials)


```{r}
# trial exclusions. Based on speedwatching + icatcher exclusion criteria
d_icatcher_trials_excluded <- d_icatcher %>% 
    filter(is.na(Trials.excludeReason)) %>% #if reason given by icatcher, exclude (NB: removes LTs <= 3, among others)
    filter(!is.na(Looks.duration_onLooks)) #inspected all NAs


d_icatcher_test_trials_excluded <- d_icatcher_trials_excluded %>% 
  filter(!SubjectInfo.subjID %in% c("sub-LIU_TLAO_s029", "sub-LIU_TLAO_s038", "sub-LIU_TLAO_s039", "sub-LIU_TLAO_s049",
                                    "sub-LIU_TLAO_s062", "sub-LIU_TLAO_s067", "sub-LIU_TLAO_s069",  "sub-LIU_TLAO_s071")) %>% 
  filter(!Looks.duration_onLooks <= 3) #for some reason icatcher did not exclude many of these guys

# Excluded subjects:
#s029 had technical difficulties
#s038 has only 2 remaining test trials and both are "unexp-flip"
#s039 nonconsecutive remaining trials: trial 11(exp-flip) and trial 14 (unexp-flip)
#s049 nonconsecutive remaining trials: trial 11(exp-flip) and trial 14 (unexp-flip)
#s062 has only 1 test trial remaining
#s067 3 remaining test trials (last pair), trial 11 (unexp), trial 13 (unexp) and trial 14 (exp). Excluding whole participant
#s069 remaining test trials are last 2: trial 13 (exp-flip) and trial 14 (unexp-flip). Excluding whole participant
#s071 has 0 test trials remaining after exclusions

# Did not exclude, but worth discussing = Subjects with 3 remaining test trials (at least 2 are consecutive):
#s034: 11 exp, 12 unexp, 14 unexp
#s036: 11 exp, 12 unexp, 13 exp
#s054: 11 unexp-flip, 12 exp-flip, 13 unexp-flip
#s056: 11 unexp, 12 exp, 14 exp
#s059: 11 unexp, 12 exp, 13 unexp
#s060: 11 unexp-flip, 12 exp-flip, 13 unexp-flip
#s083: 11 exp-flip, 12 unexp-flip, 14 unexp-flip
#s075: 11, 12, 14 

# If we exclude triplets and only remained with pairs: (no difference to outcome):
# d_icatcher_test_trials_excluded <- d_icatcher_test_trials_excluded %>%
#   filter(!(SubjectInfo.subjID == "sub-LIU_TLAO_s034" & Trials.ordinal == "14")) %>%
#   filter(!(SubjectInfo.subjID == "sub-LIU_TLAO_s036" & Trials.ordinal == "13")) %>%
#   filter(!(SubjectInfo.subjID == "sub-LIU_TLAO_s054" & Trials.ordinal == "13")) %>%
#   filter(!(SubjectInfo.subjID == "sub-LIU_TLAO_s056" & Trials.ordinal == "14")) %>%
#   filter(!(SubjectInfo.subjID == "sub-LIU_TLAO_s059" & Trials.ordinal == "13")) %>%
#   filter(!(SubjectInfo.subjID == "sub-LIU_TLAO_s060" & Trials.ordinal == "13")) %>%
#   filter(!(SubjectInfo.subjID == "sub-LIU_TLAO_s075" & Trials.ordinal == "14")) %>%
#   filter(!(SubjectInfo.subjID == "sub-LIU_TLAO_s083" & Trials.ordinal == "14"))

```


## Wrangle data for plotting

```{r, fig.width = 10}
d_icatcher_plot <-  d_icatcher_test_trials_excluded %>%
  #add age
  left_join(d_pyhab %>%
              select(sID, months, days, condLabel, sex) %>%
              distinct(sID, .keep_all = TRUE) %>%  #
              rename(SubjectInfo.subjID = "sID"),
            by = "SubjectInfo.subjID") %>%
  mutate(months = ifelse(SubjectInfo.subjID == "sub-LIU_TLAO_s032", 8, months)) %>%
  mutate(months = ifelse(SubjectInfo.subjID == "sub-LIU_TLAO_s070", 8, months)) %>%
  filter(!months > 8) %>%  #exclude one 9-month-old
  mutate(age_months_decimal = months + (days / 30.44)) %>%
  mutate(age_median = median(age_months_decimal, na.rm = TRUE),
         age_split = case_when(age_months_decimal >= age_median ~ "older",
                               TRUE ~ "younger")) %>%
  select(-age_median) %>% 
  mutate(sex = ifelse(sex == "f", "F", sex)) %>% 
  #do rest of wrangling
  filter(!Trials.verboseTrialType %in% c("calib-short", "calib-long", "audio-test")) %>%
  mutate(trialType = case_when(Trials.verboseTrialType %in% c("train-flip", "train") ~ "train",
                               Trials.verboseTrialType %in% c("fam-flip", "fam") ~ "fam",
                               Trials.verboseTrialType %in% c("unexp", "unexp-flip") ~ "unexpected",
                               Trials.verboseTrialType %in% c("exp", "exp-flip") ~ "expected",
                               TRUE ~ Trials.verboseTrialType)) %>%
  group_by(SubjectInfo.subjID) %>%
  mutate(fam_index = cumsum(trialType == "fam"),
         train_index = cumsum(trialType == "train"),
         exp_index = cumsum(trialType == "expected"),
         unexp_index = cumsum(trialType == "unexpected"),
         n_trialType = case_when(trialType == "fam" ~ str_c("fam ", fam_index),
                                 trialType == "train" ~ str_c("train ", train_index),
                                 trialType == "expected" ~ str_c("expected ", exp_index),
                                 trialType == "unexpected" ~ str_c("unexpected ", unexp_index),
                                 TRUE ~ trialType)) %>%
  select(-fam_index, -train_index, -exp_index, -unexp_index) %>%
  ungroup() %>%
  mutate(n_trialType = factor(n_trialType, levels = c("train 1", "fam 1", "train 2", "fam 2", 
                                                      "train 3", "fam 3", "train 4", "fam 4", 
                                                      "expected 1", "unexpected 1", "expected 2", "unexpected 2")),
         trials_famhab = factor(ifelse(n_trialType %in% c("expected 1", "unexpected 1", "expected 2", "unexpected 2"),
                                       "test", "famhab"))) %>%
  group_by(SubjectInfo.subjID) %>%
  mutate(trains_n = cumsum(Trials.trialType == "train"),
         max_trains = max(trains_n, na.rm = TRUE),
         tests_n = cumsum(Trials.trialType == "test"),
         max_tests = max(tests_n, na.rm = TRUE),
         fams_n = cumsum(Trials.trialType == "fam"),
         max_fams = max(fams_n, na.rm = TRUE)) %>%
  ungroup()

```


## Exploratory checks

```{r}
# plot remaining train trials
d_icatcher_plot %>% 
  distinct(SubjectInfo.subjID, max_trains) %>% 
  ggplot(aes(x = max_trains)) +
  geom_histogram(binwidth = .5, aes(fill = factor(max_trains))) +
  geom_text(stat = "count", aes(label = ..count..), vjust = -0.5, color = "black") +
  theme_bw() +
  labs(title = "Distribution of train trials histogram",
       x = "Number of train trials") +
  theme(legend.position = "none")

# Plot looking times facetted by number train trials
d_icatcher_plot %>% 
  mutate(max_trains = as.factor(max_trains)) %>% 
  ggplot(aes(x = n_trialType, y = Looks.duration_onLooks, fill = trials_famhab)) +
  geom_boxplot(outliers = FALSE) +
  geom_point(aes(group = SubjectInfo.subjID, color = SubjectInfo.subjID), alpha = 2, size = 3) +
  geom_line(aes(group = SubjectInfo.subjID), alpha = .2, linewidth = .5) +
  theme_bw() +
  theme(legend.position = "none") +
  labs(y = "Looking Time (secs)",
       x = "Trial") +
  theme(axis.text.x = element_text(angle = 90)) +
  facet_wrap(~max_trains)

# plot how many remaining TESTS trials
d_icatcher_plot %>% 
  distinct(SubjectInfo.subjID, max_tests) %>% 
  ggplot(aes(x = max_tests)) +
  geom_histogram(binwidth = .5) +
  geom_text(stat = "count", aes(label = ..count..), vjust = -0.5, color = "black") +
  theme_bw() +
  labs(x = "remaining test trials")
```


# Plots 

## Age, Conditions

```{r}
#N
d_icatcher_plot %>% 
  distinct(SubjectInfo.subjID) %>% 
  summarize(n = n())

#age
d_icatcher_plot %>% 
  distinct(SubjectInfo.subjID, months) %>% 
  mutate(months = factor(months)) %>% 
  ggplot(aes(x = months, fill = months)) +
  geom_bar() +
  geom_text(stat = "count", aes(label = after_stat(count)), vjust = -0.5) +  # Updated with after_stat()
  theme_bw() +
  scale_fill_brewer(palette = "Greens") +
  theme(legend.position = "none") 

range(d_icatcher_plot$age_months_decimal)
mean(d_icatcher_plot$age_months_decimal)


#sex
d_icatcher_plot %>% 
  distinct(SubjectInfo.subjID, sex) %>% 
  mutate(sex = factor(sex)) %>% 
  ggplot(aes(x = sex, fill = sex)) +
  geom_bar() +
  geom_text(stat = "count", aes(label = after_stat(count)), vjust = -0.5) +  # Updated with after_stat()
  theme_bw() +
  scale_fill_brewer(palette = "Greens") +
  theme(legend.position = "none") 

#conditions
d_icatcher_plot %>% 
  distinct(SubjectInfo.subjID, condLabel) %>% 
  mutate(condLabel = factor(condLabel)) %>% 
  ggplot(aes(x = condLabel, fill = condLabel)) +
  geom_bar() +
  geom_text(stat = "count", aes(label = after_stat(count)), vjust = -0.5) +  # Updated with after_stat()
  theme_bw() +
  scale_fill_brewer(palette = "Blues") +
  theme(legend.position = "none")
```


## Plot all trials

```{r, fig.width = 8}

plot_all_trials <- d_icatcher_plot %>% 
  ggplot(aes(x = n_trialType, y = Looks.duration_onLooks, fill = trials_famhab)) +
  geom_boxplot(outliers = FALSE) +
  geom_point(aes(group = SubjectInfo.subjID, color = SubjectInfo.subjID), alpha = 2, size = 3) +
  geom_line(aes(group = SubjectInfo.subjID), alpha = .2, linewidth = .5) +
  stat_summary(fun = "mean", geom = "point", shape = 23, fill = "white", size = 3) +
  theme_bw() +
  theme(legend.position = "none") +
  labs(y = "Looking Time (secs)",
       x = "Trial") +
  theme(axis.text.x = element_text(angle = 90)) 

plot_all_trials 
 

# ggsave(filename = here("figures", "iCatcher_allTrials.pdf"),
#        width = 10,
#        height = 6)

```

## Plot only test events


```{r}
d_icatcher_plot %>% 
  filter(Trials.trialType == "test") %>% 
  filter(n_trialType %in% c("unexpected 1", "expected 1")) %>% #works for msx tests of 2, 3, and 4
  ggplot(aes(x = n_trialType, y = Looks.duration_onLooks)) +
  geom_boxplot(outliers = FALSE) +
  geom_point(aes(group = SubjectInfo.subjID), alpha = .2, size = 4) +
  geom_line(aes(group = SubjectInfo.subjID), alpha = .2, linewidth = 1) +
  #stat_summary(fun.data = "mean_se", geom = "errorbar", width = .5) +
  stat_summary(fun = "mean", geom = "point", shape = 23, fill = "white", size = 5) +
  theme_bw() +
  theme(legend.position = "none") +
  labs(y = "Looking Time (secs)",
       x = "Trial") +
  theme(axis.text = element_text(size = 14),
        axis.title = element_text(size = 14)) 

# mean and sd raw values
d_icatcher_plot %>% 
  filter(Trials.trialType == "test") %>%
  filter(n_trialType %in% c("unexpected 1", "expected 1")) %>% #works for msx tests of 2, 3, and 4
  group_by(trialType) %>% 
  summarize(mean = mean(Looks.duration_onLooks), sd = sd(Looks.duration_onLooks))

```


# Exploring training effect 

## median splitting training time

```{r, fig.width = 10}
d_plot <- d_icatcher_plot %>%
  # filter(!n_trialType %in% c("expected 2", "unexpected 2")) %>%
  group_by(SubjectInfo.subjID, Trials.trialType) %>%
  mutate(aggregate_trial = sum(Looks.duration_onLooks)) %>%
  ungroup() %>%
  mutate(d_expl_short_median = median(aggregate_trial[Trials.trialType == "train"], na.rm = TRUE)) %>%
  mutate(train_duration = ifelse(
    Trials.trialType == "train" & aggregate_trial > d_expl_short_median,
    "train longer than median",
    "train shorter than median")) %>%
  group_by(SubjectInfo.subjID) %>%
  mutate(train_duration = first(train_duration[Trials.trialType == "train"])) %>%
  ungroup() %>%
  relocate(train_duration, .after = "d_expl_short_median") %>%
  relocate(Looks.duration_onLooks, .after = "train_duration") %>%
  relocate(aggregate_trial, .after = "Looks.duration_onLooks")

d_plot %>% 
  filter(!n_trialType %in% c("unexpected 2", "expected 2")) %>% #works for msx tests of 2, 3, and 4
  ggplot(aes(x = n_trialType, y = Looks.duration_onLooks, fill = trials_famhab)) +
  geom_boxplot(outliers = FALSE) +
  geom_point(aes(group = SubjectInfo.subjID, color = SubjectInfo.subjID), alpha = 2, size = 3) +
  geom_line(aes(group = SubjectInfo.subjID), alpha = .2, linewidth = .5) +
  stat_summary(fun = "mean", geom = "point", shape = 23, fill = "white", size = 3) +
  theme_bw() +
  theme(legend.position = "none") +
  labs(y = "Looking Time (secs)",
       x = "Trial") +
  theme(axis.text.x = element_text(angle = 90)) +
  theme(legend.position = "none",
        axis.text = element_text(size = 14),
        axis.title = element_text(size = 14),
        strip.text = element_text(size = 15)) +
  facet_wrap(~train_duration)

```
# trianing effect linear model

```{r}
d_voe <- d_plot %>%
  filter(n_trialType %in% c("expected 1", "unexpected 1")) %>%
  group_by(SubjectInfo.subjID, n_trialType, train_duration) %>%
  summarise(mean_looking_time = mean(Looks.duration_onLooks, na.rm = TRUE), .groups = "drop") %>%
  pivot_wider(
    names_from = n_trialType,
    values_from = mean_looking_time,
    names_prefix = "mean_"
  ) %>%
  mutate(voe_effect = `mean_unexpected 1` - `mean_expected 1`)

# Fit linear model: Does train_duration predict VOE effect?
model <- lm(voe_effect ~ train_duration, data = d_voe)

# Summarize the model
summary(model)

```


## correlation between training time and voe effect

```{r, fig.width = 9}
d_plot_corr <- d_plot %>% 
  group_by(SubjectInfo.subjID) %>%
  mutate(aggregate_train = sum(Looks.duration_onLooks[Trials.trialType == "train"], na.rm = TRUE)) %>%
  # mutate(aggregate_train = aggregate_trial[Trials.trialType == "train"][1]) %>% 
  relocate(aggregate_train, .after = "aggregate_trial") %>% 
  ungroup() %>% 
  mutate(log_looks = log(Looks.duration_onLooks)) %>% #get log looks
  filter(n_trialType %in% c("expected 1", "unexpected 1")) %>%
  filter(SubjectInfo.subjID != "sub-LIU_TLAO_s049") %>% #only has 1 rem trial after filtering down
  group_by(SubjectInfo.subjID) %>%
  mutate(
    log_expected_1 = max(ifelse(n_trialType == "expected 1", log_looks, NA), na.rm = TRUE),
    log_unexpected_1 = max(ifelse(n_trialType == "unexpected 1", log_looks, NA), na.rm = TRUE),
    logarithmic_difference = log_unexpected_1 - log_expected_1) %>%
  ungroup()

# plot
plot_corr_training_voe <- ggplot(d_plot_corr, aes(x = aggregate_train, y = logarithmic_difference)) +
  geom_point(aes(color = SubjectInfo.subjID)) +  
  geom_hline(yintercept = 0, linetype = "dashed") +  
  geom_smooth(method = "lm", se = TRUE, color = "blue") +  
  labs(x = "Cumulative Train Duration (Seconds)",
       y = "Log Looking Time (Unexpected - Expected)") +
  theme_bw() +
  theme(legend.position = "none",
        axis.text = element_text(size = 14),
        axis.title = element_text(size = 14))


plot_corr_training_voe 

# Fit the linear model
# model_corr <- lm(logarithmic_difference ~ aggregate_train, data = d_plot_corr)

# Summarize the results
# summary(model_corr)

```

# age differences in correlations

```{r, fig.width = 9}
plot_corr_training_voe + facet_wrap(~age_split) + theme(strip.text = element_text(size = 15))

model_corr <- lm(logarithmic_difference ~ aggregate_train, data = d_plot_corr)

```


## Plot all trials with median age split

```{r, fig.width = 8}
plot_all_trials <- d_icatcher_plot %>% 
  filter(!n_trialType %in% c("unexpected 2", "expected 2")) %>% #works for msx tests of 2, 3, and 4
  ggplot(aes(x = n_trialType, y = Looks.duration_onLooks, fill = trials_famhab)) +
  geom_boxplot(outliers = FALSE) +
  geom_point(aes(group = SubjectInfo.subjID, color = SubjectInfo.subjID), alpha = 2, size = 3) +
  geom_line(aes(group = SubjectInfo.subjID), alpha = .2, linewidth = .5) +
  stat_summary(fun = "mean", geom = "point", shape = 23, fill = "white", size = 3) +
  theme_bw() +
  theme(legend.position = "none") +
  labs(y = "Looking Time (secs)",
       x = "Trial") +
  theme(axis.text.x = element_text(angle = 90)) +
  theme(legend.position = "none",
        axis.text = element_text(size = 14),
        axis.title = element_text(size = 14),
        strip.text = element_text(size = 15)) +
  facet_wrap(~age_split) 


plot_all_trials 

# ggsave(filename = here("figures", "iCatcher_allTrials.pdf"),
#        width = 10,
#        height = 6)

```

## Plot test trials

```{r}
plot_test_trials <- d_icatcher_plot %>% 
  filter(trials_famhab != "famhab") %>% 
  filter(!n_trialType %in% c("unexpected 2", "expected 2")) %>% #works for msx tests of 2, 3, and 4
  ggplot(aes(x = n_trialType, y = Looks.duration_onLooks)) +
  geom_boxplot(aes(fill = trialType), outliers = FALSE) +
  geom_line(aes(group = SubjectInfo.subjID), alpha = .1, linewidth = .5) +
  geom_point(aes(group = SubjectInfo.subjID, color = SubjectInfo.subjID), alpha = .6, size = 4) +
  stat_summary(fun = mean, geom = "point", shape = 23, fill = "white", size = 4) +
  theme_bw() +
  labs(y = "Looking Time",
       x = "Trial") +
  theme(legend.position = "none",
        axis.text.x = element_text(size = 12),
        axis.title.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        strip.text = element_text(size = 15)) +
  facet_wrap(~age_split)

plot_test_trials

# ggsave(filename = here("figures", "iCatcher_allTests.pdf"))

```

## Plot test trials by condition

```{r, fig.width = 8, fig.height = 6}
d_icatcher_plot %>% 
  filter(trials_famhab != "famhab") %>% 
  mutate(condition = case_when(condLabel == 1 ~ "1: fam-flip last <-, exp-flip first ->",
                               condLabel == 2 ~ "2: fam last ->, unexp first ->",
                               condLabel == 3 ~ "3: fam last ->, unexp-flip first <-",
                               condLabel == 4 ~ "4: fam-flip last <-, exp first <-")) %>% 
  ggplot(aes(x = n_trialType, y = Looks.duration_onLooks)) +
  geom_boxplot(aes(fill = trialType), outliers = FALSE) +
  geom_point(aes(group = SubjectInfo.subjID), alpha = .2, size = 4) +
  geom_line(aes(group = SubjectInfo.subjID), alpha = .2, linewidth = .5) +
  stat_summary(fun = mean, geom = "point", shape = 23, fill = "white", size = 4) +
  theme_bw() +
  labs(y = "Looking Time",
       x = "Trial") +
  theme(legend.position = "none",
        axis.text.x = element_text(size = 12),
        axis.title.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.y = element_text(size = 12)) +
  facet_wrap(vars(condition)) + 
  theme(axis.text.x = element_text(angle = 90))

```

## conditions again, different labels


```{r}
d_icatcher_plot %>% 
  filter(trials_famhab != "famhab") %>% 
  filter(!n_trialType %in% c("unexpected 2", "expected 2")) %>% 
  mutate(condition = case_when(condLabel %in% c(1, 4) ~ "expected first", #cond 1 and 4
                               TRUE ~ "unexpected first")) %>% #cond 2 and 3
  ggplot(aes(x = n_trialType, y = Looks.duration_onLooks)) +
  geom_boxplot(aes(fill = trialType), outliers = FALSE) +
  geom_line(aes(group = SubjectInfo.subjID), alpha = .1, linewidth = .5) +
  geom_point(aes(group = SubjectInfo.subjID, color = SubjectInfo.subjID), alpha = .6, size = 4) +
  stat_summary(fun = mean, geom = "point", shape = 23, fill = "white", size = 4) +
  theme_bw() +
  labs(y = "Looking Time (seconds)",
       x = "Trial") +
  theme(legend.position = "none",
        axis.text.x = element_text(size = 12),
        axis.title.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        strip.text = element_text(size = 15)) +
  facet_wrap(vars(condition)) 

# ggsave(filename = here("figures", "iCatcher_allTests.pdf"))

```

## Plot first test pair

```{r}
d_icatcher_plot_first_pair <- d_icatcher_plot %>% 
  filter(!(Trials.ordinal %in% c(13, 14)))

plot_first_test_pair <- d_icatcher_plot_first_pair %>% 
  filter(trials_famhab != "famhab") %>% 
  # filter(n_trialType %in% c("unexpected 1", "expected 1")) %>% 
  ggplot(aes(x = n_trialType, y = Looks.duration_onLooks)) +
  geom_boxplot(aes(fill = n_trialType), outliers = FALSE) +
  geom_line(aes(group = SubjectInfo.subjID), alpha = .2, linewidth = .5) +
  geom_point(aes(group = SubjectInfo.subjID, color = SubjectInfo.subjID), alpha = .6, size = 4) +
  stat_summary(fun = mean, geom = "point", shape = 23, fill = "white", size = 4) +
  theme_bw() +
  labs(y = "Looking Time (Seconds)",
       x = "Trial") +
  theme(legend.position = "none",
        axis.text.x = element_text(size = 12),
        axis.title.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.y = element_text(size = 12))

plot_first_test_pair

## ggsave(filename = here("figures", "iCatcher_firstTestPair.pdf"))
```

# Statistical analysis

```{r, echo = TRUE, fig.width = 8, fig.height = 6}
d_icatcher_stats <- d_icatcher_plot_first_pair %>% 
  filter(Trials.trialType == "test") %>% 
  mutate(order = ifelse(condLabel %in% c(1, 4), "expected_first", "unexpected_first")) %>% 
  filter(!is.nan(Log_looks) & !is.infinite(Log_looks)) %>% 
  mutate(Index = row_number())

model <- lmer(Looks.duration_onLooks ~ trialType + (1 | SubjectInfo.subjID), data = d_icatcher_stats)
summary(model)

performance::check_model(model)

```

#with log-transformation

```{r, echo = TRUE, fig.width = 8, fig.height = 6}
model_log <- lmer(Log_looks ~ trialType + (1 | SubjectInfo.subjID) + age_months_decimal + order, data = d_icatcher_stats)
summary(model_log)

performance::check_model(model_log)

```






